Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-10-28 paper/main.tex
changed V V* diagram

\subsubsection{Data to Visual Encodings: \vchannel} 
\begin{equation}
  \label{eq:artist:construction:nu}
\begin{tikzcd}
  \textcolor{gray!50}{\dtotal} \arrow[rd, "\pi"'] \arrow[r, "\vchannel"] & \vtotal \arrow[d, "\pi"] & \vindex^*\vtotal \arrow[d, "\vindex^*\pi"', color=gray!50] \arrow[l, "\vindex^*", color=gray!50] & \textcolor{gray!50}{\gtotal} \arrow[ld, "\pi", color=gray!50] \\
& \dbase                   & \textcolor{gray!50}{\gbase} \arrow[l, "\vindex"', color=gray!50]                                       &                          
  \end{tikzcd}
\end{equation}

@@

We enforce the equivariance constraint specified in \autoref{eq:artist:construction:multi_nu} by constructing artists that apply \vchannel\ encoders such that 
\begin{equation}
  \label{eq:artist:construction:multi_nu}
  \begin{tikzcd}[row sep=.5em]
    \dfiber_a \arrow[rrd, "proj_a" description] \arrow[rrrr, "\vchannel_{\dfiber_c}"]          &  &                                                                                                                        &  & \vfiber_{\dfiber_c}          \\
    &  & \dfiber_{c} \arrow[rru, "\vchannel_{\dfiber_c}" description] \arrow[rrd, "\vchannel^{\prime}_{\dfiber_c}" description] &  &                              \\
\dfiber_b \arrow[rru, "proj_b" description] \arrow[rrrr, "\vchannel^{\prime}_{\dfiber_c}"] &  &                                                                                                                        &  & \vfiber^{\prime}_{\dfiber_c}
    \end{tikzcd}
\end{equation}

\subsubsection{Visual to Graphic: \vmark} 
\begin{equation}
  \label{eq:artist:construction:q}
  \begin{tikzcd}
    \textcolor{gray!50}{\dtotal} \arrow[rd, "\pi"', color=gray!50] \arrow[r, "\vchannel", color=gray!50] & \textcolor{gray!50}{\vtotal} \arrow[d, "\pi", color=gray!50] & \vindex^*\vtotal \arrow[d, "\vindex^*\pi"'] \arrow[l, "\vindex^*"', color=gray!50] \arrow[r, "\vmark"] & \gtotal \arrow[ld, "\pi"] \\
    & \dbase & \gbase \arrow[l, "\vindex"', color=gray!50]                                            &                          
    \end{tikzcd}
\end{equation}

\begin{equation}
  \label{eq:artist:construction:q:xi}
  \begin{tikzcd}[column sep= 1em, row sep=.7em]
    \vtotal \arrow[rrd, "\hat{\vmark}"]                             &  &         \\
                                                                    &  & \gtotal \\
    \vindex^*\vtotal \arrow[uu, "\vindex^*"] \arrow[rru, "\vmark"'] &  &        
    \end{tikzcd}
\end{equation}

>>>>

\subsubsection{Data to Visual Encodings: \vchannel} 
\begin{equation}
  \label{eq:artist:construction:nu}
\begin{tikzcd}
  \dtotal \arrow[rd, "\pi"'] \arrow[r, "\vchannel"] & \vtotal \arrow[d, "\pi"] & \textcolor{fade}{\vindex^*\vtotal} \arrow[d, "\vindex^*\pi"', color=fade] \arrow[l, "\vindex^*", color=fade] & \textcolor{fade}{\gtotal} \arrow[ld, "\pi", color=fade] \\
& \dbase                   & \textcolor{gray!50}{\gbase} \arrow[l, "\vindex"', color=gray!50]                                       &                          
  \end{tikzcd}
\end{equation}

@@

We enforce the equivariance constraint specified in \autoref{eq:artist:construction:multi_nu} by constructing artists that apply \vchannel\ encoders such that 
\begin{equation}
  \label{eq:artist:construction:multi_nu}
  \begin{tikzcd}[row sep=.5em]
    \dfiber_a \arrow[rrd, "proj_a" description] \arrow[rrrr, "\vchannel_{\dfiber_c}"]           &  &  &  & \vfiber_{\dfiber_c}          \\
     &  & \dfiber_{c} \arrow[rru, "\vchannel_{\dfiber_c}" description] \arrow[rrd, "\vchannel^{\prime}_{\dfiber_c}" description] &  &                              \\
    \dfiber_b \arrow[rru, "proj_b" description] \arrow[rrrr, "\vchannel^{\prime}_{\dfiber_c}"'] &  &                                                                                                                        &  & \vfiber^{\prime}_{\dfiber_c}
    \end{tikzcd}
\end{equation}

\subsubsection{Visual to Graphic: \vmark} 
\begin{equation}
  \label{eq:artist:construction:q}
  \begin{tikzcd}
    \textcolor{fade}{\dtotal} \arrow[rd, "\pi"', color=fade] \arrow[r, "\vchannel", color=fade] & \textcolor{gray!50}{\vtotal} \arrow[d, "\pi", color=fade] & \vindex^*\vtotal \arrow[d, "\vindex^*\pi"'] \arrow[l, "\vindex^*"', color=fade] \arrow[r, "\vmark"] & \gtotal \arrow[ld, "\pi"] \\
    & \textcolor{fade}{\dbase} & \gbase \arrow[l, "\vindex"', color=fade]                                            &                          
    \end{tikzcd}
\end{equation}

\begin{equation}
  \label{eq:artist:construction:q:xi}
  \begin{tikzcd}
    \vtotalc \arrow[rr, "\vmarkdc", bend left] & \vtotalpullc \arrow[l, "\vindexc^*"] \arrow[r, "\vmarkc"'] & \gtotalc
  \end{tikzcd}
\end{equation}
